\subsection{Basic IO}
    \lstinputlisting{java/basic_io.java}
\subsection{Fast Input}
    \lstinputlisting{java/fast_input.java}
\subsection{java.lang.String}
    \subsubsection{Constructor}
        \lstinline[language=Java]{String(String original)}\\
        Initializes a newly created String object that is a copy of the argument string.

        \noindent
        \lstinline[language=Java]{String(StringBuffer buffer)}\\
        Allocates a new string that contains the sequence of characters currently contained in the string buffer argument.

        \noindent
        \lstinline[language=Java]{String(StringBuilder builder)}\\
        Allocates a new string that contains the sequence of characters currently contained in the string builder argument.
    \subsubsection{Methods}
        \lstinline[language=Java]{boolean equals(Object anObject)}\\
        只當參數非空且字串內字元組成相等才回傳true。

        \noindent
        \lstinline[language=Java]{int compareTo(String anotherString)}\\
        回傳字典序比較結果(以UTF-8編碼比較)\\
        負數: 參數<this\\
        正數: 參數>this\\
        0: 相等

        \noindent
        \lstinline[language=Java]{boolean isEmpty()}
        
        \noindent
        \lstinline[language=Java]{int length()}

        \noindent
        \lstinline[language=Java]{int indexOf(String str, int fromIndex)}\\
        Returns the index within this string of the \textbf{first occurrence} of the specified character/substring.

        \noindent
        \lstinline[language=Java]{char charAt(int index)}\\
        Returns the char value at the specified index. An index ranges starts from 0.

        \noindent
        \lstinline[language=Java]{String concat(String str)}\\
        回傳相接後的字串

        \noindent
        \lstinline[language=Java]{String replace(char oldChar, char newChar)}

        \noindent
        \lstinline[language=Java]{String toLowerCase()}

        \noindent
        \lstinline[language=Java]{String toUpperCase()}

        \noindent
        \lstinline[language=Java]{String trim()}\\
        Returns a copy of the string, with leading and trailing whitespace omitted.

        \noindent
        \lstinline[language=Java]{String toString()}\\
        this string itself.


        \noindent
        \lstinline[language=Java]{String[] split(String regex)}\\
        return string array that seperate original string by given regex.

\subsection{BigInteger \& Big Decimal}

    \subsubsection{Static}
        \begin{itemize}
        \item \lstinline{BigInteger} \& \lstinline{BigDecimal}\\
        ONE / TEN / ZERO
        \item \lstinline{BigDecimal} (type is int)\\
        ROUND\_CEILING -> $+\infty$\\
        ROUND\_FLOOR -> $-\infty$\\
        ROUND\_DOWN -> $0$ (to)\\
        ROUND\_UP <- $0$ (away)\\
        ROUND\_HALF\_DOWN / ROUND\_HALF\_UP -> nearest -> down/ up\\
        ROUND\_UNNECESSARY assert no round needed\\
        \end{itemize}
    \subsubsection{Static Method}
        \lstinline{BigInt/BigDecimal valueOf(long/\[double\] val)} 只有BigDecimal能傳double

    \subsubsection{Constructor}
        \lstinline{BigInteger/BigDecimal(String val)}
        \lstinline{BigDecimal(int/long/double val)}

    \subsubsection{Similar Method}
        \lstinline{int compareTo(BigInteger val)} -1, 0, 1 是指 <, =, >\\
        \lstinline{boolean equals(Object val)} numerical equal\\
        \lstinline{double doubleValue()}, \lstinline{int intValue()}\\
        \lstinline{String toString()}\\
        \lstinline{abs / negate()}\\
        \lstinline{min / max(BigInteger/BigDecimal val)}\\
        \lstinline{add/substract/multiply(BigInteger/BigDecimal val)}\\
        \lstinline{pow(BigInteger/BigDecimal val)} this\^val\\
        \lstinline{BigInteger/BigDecimal[] divideAndRemainder(BigInteger/BigDecimal val)}\\
        \lstinline{int signum()}\\

    \subsubsection{BigInteger Method}
        \lstinline{and / andNot / or / xor (BigInteger val)} bitwise operate\\
        \lstinline{not()} not bitwise operate\\
        \lstinline{shiftLeft / shiftRight (int n)} bitwise shift\\
        \lstinline{gcd(BigInteger val)}\\
        \lstinline{divide/mod(BigInteger val)}\\
        \lstinline{boolean isProbablePrime(int certainty)} rabin-miller\\
        \lstinline{modInverse(BigInteger m)} ($this^{-1} \mod m$)\\
        回傳一個\lstinline{BigInteger[]}含有 (this / val) (this \% val)\\\
        
    \subsubsection{BigDecimal Method}
        \lstinline{divide(BigDecimal divisor)} if the exact quotient cannot be represented an `ArithmeticException` is thrown.\\
        \lstinline{divide(BigDecimal divisor, int roundingMode)} divide with rounding mode\\
        \lstinline{plus()} ++this\\
        \lstinline{int scale()} return scale\\
        \lstinline{setScale(int newScale)}\\
        \lstinline{setScale(int newScale, int roundingMode)}\\
        \lstinline{BigInteger toBigInteger[Exact]()}\\
        \lstinline{int/longValue[Exact]()}\\
        \textbf{Method End with "Exact" 會在分數部分非零時拋出算術例外}\\
    